---
title: Rmarkdown Content
author: jemus42
date: '2020-06-06'
slug: rmarkdown-content
categories: ["Rmarkdown"]
tags: []
description: ''
draft: no
externalLink: ''
series: []
output: hugodown::hugo_document
---

```{r setup}
knitr::opts_chunk$set(
  fig.path = "plots/", # for leaf bundles to work nicely
  cache = TRUE,
  cache.path = "post_cache/", # (for leaf bundles, cache in post directory)
  fig.retina = 2,
  fig.width = 8.5,
  echo = TRUE,
  message = FALSE, warning = FALSE, error = FALSE,
  fig.align = "center",
  out.width = "95%"
)
```

This is a test of {{< pkg "hugodown" >}}.  


## R Code

### Code with/-out Output

```{r}
my_packages <- rownames(installed.packages())
n_packages <- length(my_packages)
```

And some filler text between chunks.

```{r}
n_packages

tail(tibble::enframe(my_packages))
```


### Plots

- The entire chunk is contained in `<pre>` tags :(
- Tabular display of code with line numbers is set in config, but not applied here

```{r a-plot}
library(ggplot2)

ggplot(mtcars, aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point() +
  geom_smooth(method = lm, se = FALSE)
```



## Footnotes

This is a footnote in `^[inline format]` as used by [pandoc](https://pandoc.org/MANUAL.html#footnotes) but not supported by [Hugo's Goldmark](https://gohugo.io/getting-started/configuration-markup/#goldmark) ^[Hello there].  

Here's a reference-style footnote [^ref].

[^ref]: Something goldmark and pandoc can agree on.


## Math and stuff

This is text with inline math $\sum_{n=1}^{\infty} 2^{-n} = 1$ and with math blocks:

$$
\sum_{n=1}^{\infty} 2^{-n} = 1
$$

| Heading | Another heading |
| :----:  | :-------------: |
|  text   |      text       |
|  text   |      text       |
|  text   |      text       |
